Total Score

### 2023-02-03 src/MSAtotal_scores.Rmd
renamed columns and updated student weights

```{r original weights}
# weight criteria for Owen
criteria_weights_owen <- c(0.37, 0.12, 0.22, 0.07, 0.0, 0.07, 0.15)

@@

```{r student weights}
# weight criteria for students
criteria_weights_students <- c(0.18, 0.0, 0.10, 0.19, 0.17, 0.14, 0.22)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_students = cbsa,
         stud_EAL_total = cbsa) #this is just a place holder

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$total_score_students[i] = weighted.mean(cbsa_data, criteria_weights_students)
}

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50_prop = cbsa, #this is just a place holder
         score_climate50_prop_EAL = cbsa)

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$score_climate50_prop[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}

>>>>

```{r original weights, eval = FALSE}
# weight criteria for Owen
criteria_weights_owen <- c(0.37, 0.12, 0.22, 0.07, 0.0, 0.07, 0.15)

@@

```{r FINAL student weights}
# weight criteria for students
criteria_weights_students <- c(0.18, 0.0, 0.10, 0.19, 0.17, 0.14, 0.22)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(final_tot_students = cbsa,
         stud_EAL_total = cbsa,
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)) #this is just a place holder

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$final_tot_students[i] = weighted.mean(cbsa_data, criteria_weights_students)
}

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(owen_FINAL_score = cbsa, #this is just a place holder
         score_climate50_prop_EAL = cbsa)

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$owen_FINAL_score[i] = weighted.mean(cbsa_data, weights_climate50_prop) 
}
